---
title: "a6-api-report"
author: "Mequanent Shiferaw"
date: "2/20/2019"
output: html_document
---
```{r setup, include=FALSE, warning=FALSE}
library("knitr")
source("civic-info.R")
source("propublica.R")
```
This is a report about the political representatives based on the address entered. This report draws upon data from the ProPublica API and the Google Civic Data API.
As an overview, here is a summary of who represents the address given. 
```{r , echo=FALSE}
kable(political_representative())
```

##House of Representatives

the bar graph shows all of the congressional representatives (in the House of Representatives,not the Senate) for the state in which the address was given and are breakdown by gender

```{r , echo=FALSE}
testing_bar_graph$gender
```



##Representatives By Party
 
```{r , echo=FALSE}
testing_bar_graph$party
```



```{r , echo=FALSE}

```
# `r first_name` `r Last_name`
Let’s learn a bit more about one representative, Ralph Abraham. The representative is `r age` years old, and you can find them on twitter at `r twitter_account`. Interestingly, of the last 20 congressional votes, the representative was in accordance with the majority `r perecentage_data`% of the time.
